Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-31 edubots_surveys.Rnw
Refactors with knitr for figures

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)

@@

data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
@

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<gender, echo=FALSE>>=
ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<age,echo=FALSE>>=
ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<sector, echo=FALSE>>=
ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

@@

    \vspace{0.5mm}
    \begin{minipage}[t]{0.3\textwidth}
	    \centering
<<experience,echo=FALSE>>=
ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.55\textwidth}
	    \centering
<<discipline,echo=FALSE>>=
ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}
%
\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE>>=
library(forcats)
data %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

@@

\begin{figure}[!ht]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
    \end{minipage}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
    \end{minipage}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
\label{figure:chatbots_messagingorganization}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
    \end{minipage}
\end{center}
    \caption{Types of chatbots.}
\label{figure:chatbots_types}
\end{figure}

\subsection{RQ2 - Which kind of interaction do teachers prefer with their students?}

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.33\textwidth}
	    \centering
<<gender_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.33\textwidth}
	    \centering
<<age_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
% 	    \includegraphics[width=\textwidth]{figures/age_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.35\textwidth}
	    \centering
<<experience_sync, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
	    \centering
<<discipline_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
    \end{minipage}
\end{center}
    \caption{Synchronous or asynchronous interaction.}
\label{figure:chatbots_synch}
\end{figure}

>>>>

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)
library(tidyverse)

@@

survey.pilot %>%  mutate(Messaging.Organization =str_split(Messaging.Organization, ", ")) %>% unnest(cols = c(Messaging.Organization)) -> survey.pilot.MessagingOrganization

survey.pilot %>% group_by( PostCOVID.changes ) %>% filter( n() > 1 ) -> survey.pilot.postCOVID

survey.pilot %>%  mutate(ChatbotType = ifelse(Agenda == "No","","Agenda,")) %>%
  mutate(ChatbotType = ifelse(ClassMaterial == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "ClassMaterial,",sep=""))) %>%
  mutate(ChatbotType = ifelse(FAQ == "No",paste(ChatbotType, "",sep=""), paste(ChatbotType, "FAQ,",sep=""))) %>%
  mutate(ChatbotType = ifelse(Grades == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "Grades,",sep=""))) %>%
  mutate(ChatbotType = ifelse(OtherBot == "No", paste(ChatbotType, "",sep=""), paste(ChatbotType, "OtherBot,",sep=""))) %>%
  mutate(ChatbotType = substr(ChatbotType,1,nchar(ChatbotType)-1))-> survey.pilot.chatbottype
survey.pilot.chatbottype %>%  mutate(ChatbotType =str_split(ChatbotType, ",")) %>% unnest(cols = c(ChatbotType)) -> survey.pilot.ChatbotType

survey.student.interaction <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
@

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Gender, aes(x=Gender, y=freqGender, fill=Gender)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/gender.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<age,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Age, aes(x=Age, y=freqAge, fill=Age)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/age.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<sector, echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Experience, aes(x=Experience, y=freqExperience, fill=Experience)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

@@

    \vspace{0.5mm}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<experience,echo=FALSE, fig.width=3.2, fig.height=2.2>>=
ggplot(freq.Sector, aes(x=Sector, y=freqSector, fill=Sector)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/experience.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
        \centering
<<discipline,echo=FALSE, fig.width=5.75, fig.height=2.2>>=
ggplot(freq.Discipline, aes(x=Discipline, y=freqDiscipline, fill=Discipline)) + geom_bar(stat="identity")+scale_y_continuous(labels=scales::percent) + theme(axis.title.y=element_blank(),axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())
@

%       \includegraphics[width=\textwidth]{figures/discipline.pdf}
    \end{minipage}
\end{center}
    \caption{Sample population description. A total 282 teachers shown by gender, age, sector (university and vocational education), number of years of experience in education, and discipline.}
\label{figure:teachers_population}
\end{figure}
%
\begin{figure}[h!tbp]
\begin{center}
<<interaction,message=FALSE,echo=FALSE, fig.height=2.0, fig.width=4.0>>=
library(forcats)
survey.student.interaction %>%
    mutate(Age = fct_relevel(Age,"25-35", "35-45", "45-55", "> 55")) %>%
    mutate(Experience = fct_relevel(Experience, "0-05 years", "06-15 years", "16-25 years", "> 25 years" )) %>%
    group_by( Age, Experience ) %>% summarise( n = n() ) %>% mutate( freq = n/sum(n)) -> Age.vs.Experience

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<gender_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<experience_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<sector_provided, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    %----
    \vspace{0.2mm}
    \hspace{10mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<discipline_provided, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.pilot, aes(x = Provided, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
    \end{minipage}
    \hspace{10mm}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<gender_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = WhatsApp, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<experience_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = WhatsApp, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<sector_whatsapp, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = WhatsApp, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
    \end{minipage}
    \vspace{0.2mm}
    \hspace{10mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<discipline_whatsapp, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.pilot, aes(x = WhatsApp, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
    \end{minipage}
    \hspace{10mm}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<gender_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Telegram, group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<experience_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Telegram, group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.31\textwidth}
        \centering
<<sector_telegram, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.pilot, aes(x = Telegram, group = Sector)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Sector)+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
    \end{minipage}
    \vspace{0.2mm}
    \hspace{10mm}
    \begin{minipage}[t]{0.5\textwidth}
        \centering
<<discipline_telegram, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.pilot, aes(x = Telegram, group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences','Sciences','Engineering','Technology','No')))+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
    \end{minipage}
    \hspace{10mm}
\end{center}
    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use}
\end{figure}

@@

\begin{figure}[h!tbp]
\centering
<<messaging_organization, echo=FALSE, fig.width=19/2.54, fig.height=5/2.54>>=
survey.pilot.MessagingOrganization <- within(survey.pilot.MessagingOrganization, Messaging.Organization <- factor(Messaging.Organization, levels=names(sort(table(Messaging.Organization), decreasing=TRUE))))
ggplot(survey.pilot.MessagingOrganization, aes( x = Messaging.Organization, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90))+coord_flip()+ theme(axis.title.y=element_blank())
@
%\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
\label{figure:chatbots_messagingorganization}
\end{figure}

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<gender_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
survey.pilot.postCOVID <- within(survey.pilot.postCOVID, PostCOVID.changes <- factor(PostCOVID.changes, levels=names(sort(table(PostCOVID.changes), decreasing=TRUE))))
ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<sector_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<experience_covid, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
ggplot(survey.pilot.postCOVID, aes( x = PostCOVID.changes, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}

@@

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<gender_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
survey.pilot.ChatbotType <- within(survey.pilot.ChatbotType, ChatbotType <- factor(ChatbotType, levels=names(sort(table(ChatbotType), decreasing=TRUE))))
ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Gender, fill = Gender ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<sector_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Sector, fill = Sector ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/sector_chatbottype.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.85\textwidth}
        \centering
<<experience_chatbottype, echo=FALSE, fig.width=19/2.54, fig.height=5.5/2.54>>=
ggplot(survey.pilot.ChatbotType, aes( x = ChatbotType, y = ..count.., group=Experience, fill = Experience ) ) + geom_bar()+ theme(axis.text.x = element_text(angle = 90)) +coord_flip()+ theme_tufte()+ theme(axis.title.y=element_blank())
@       
%       \includegraphics[width=\textwidth]{figures/experience_chatbottype.pdf}
    \end{minipage}
\end{center}
    \caption{Types of chatbots.}
\label{figure:chatbots_types}
\end{figure}

\subsection{RQ3 - Which kind of interaction do teachers prefer with their students?}

\begin{figure}[h!tbp]
\begin{center}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<gender_synch, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.3\textwidth}
        \centering
<<experience_sync, echo=FALSE, fig.width=10/2.54, fig.height=7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
        \centering
<<discipline_synch, echo=FALSE, fig.width=18.6/2.54, fig.height=7.7/2.54>>=
ggplot(survey.student.interaction, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
%       \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
    \end{minipage}
\end{center}
    \caption{Synchronous or asynchronous interaction.}
\label{figure:chatbots_synch}
\end{figure}
